Trends of SDR in Thessaloniki

### 2023-07-10 Article.Rmd
Commit 2023-07-10 17:14

```{r cumsum, echo = FALSE, fig.cap='Running plots of the cumulative sum of the daily SDR for three different sky conditions', fig.subcap=c('All-sky conditions', 'Clear-sky conditions', 'Cloud-sky conditions'), out.width='.32\\linewidth', fig.asp=1, fig.ncol = 3}
knitr::include_graphics(c(
    "./images/CumulativeDailyCumSum-1.png",    # ALL sky
    "./images/CumulativeDailyCumSum-5.png",    # CLEAR sky
    "./images/CumulativeDailyCumSum-9.png"))   # Cloud sky
```

@@

@@

<!-- ```{r , echo=F, fig.cap="All sky"} -->
<!-- knitr::include_graphics("./images/SzaTrends-5.png") -->
<!-- ``` -->

<!--
```{r , echo=F, fig.cap="Clear sky"}
knitr::include_graphics("./images/SzaTrends-13.png")
```
-->

<!-- ```{r , echo=F, fig.cap="Cloud sky"}
knitr::include_graphics("./images/SzaTrends-21.png")
``` -->

```{r szatrends, echo = FALSE, fig.cap='Distribution of the SDR\'s long term trends by SZA.', fig.subcap=c('Trend distribution for all-sky conditions.', 'Trend distribution for cloud-sky conditions.'), out.width='.35\\linewidth', fig.asp=1, fig.ncol = 2}
knitr::include_graphics("./images/SzaTrends-13.png")
knitr::include_graphics("./images/SzaTrends-21.png")
```

>>>>

```{r cumsum, echo = FALSE, fig.cap='Running cumulative sum plots of the daily SDR for three different sky conditions', fig.subcap=c('All-sky conditions', 'Clear-sky conditions', 'Cloud-sky conditions'), out.width='.32\\linewidth', fig.asp=1, fig.ncol = 3}
knitr::include_graphics(c(
    "./images/CumulativeDailyCumSum-1.png",    # ALL sky
    "./images/CumulativeDailyCumSum-5.png",    # CLEAR sky
    "./images/CumulativeDailyCumSum-9.png"))   # Cloud sky
```

@@

We group the anomaly data in $1^\circ$ SZA bins, and calculate the overall trend for each bin

@@

```{r szatrends, echo = FALSE, fig.cap='Distribution of the SDR\'s long term trends by SZA.', fig.subcap=c('Trend distribution for all-sky conditions.', 'Trend distribution for cloud-sky conditions.'), out.width='.35\\linewidth', out.width='.32\\linewidth', fig.asp=1, fig.ncol = 3}
knitr::include_graphics("./images/SzaTrends-13.png")
knitr::include_graphics("./images/SzaTrends-17.png" )
knitr::include_graphics("./images/SzaTrends-21.png")
```
